---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# codestral

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

Thanks to an appropriate Rstudio addin, this package allows prompting [Mistra AI](https://mistral.ai/) models using their API for fill in the middle (FIM) and chat in Rstudio. With this package, one can create an Addin in Rstudio that allows a direct and simple use of the Mistral AI API.

For FIM, the [Codestral](https://mistral.ai/news/codestral) model is used.

For chatting, the user may use either Codestral or [Codestral Mamba](https://mistral.ai/news/codestral-mamba).

## Installation

You should first get 2 API keys from the Mistral AI [Plateforme](https://mistral.ai/news/la-plateforme):

- one general Mistral AI API key (menu `API` in La Plateforme).
- one Codestral API key (menu `Codestral` in La Plateforme).

You can install the development version of codestral from [GitHub](https://github.com/comevussor/codestral) with:

``` r
# install.packages("pak")
pak::pak("comevussor/codestral")
```
Restart your session to activate the addin.

## Set up for usage in Rstudio

The package needs to be initialized, especially to get your API key.

```{r example}
library(codestral)
## basic example code

# replace *** with your API key
# codestral_init(apikey = "********************************")
```

## Starting example

Open a new text file and type: `"m: Hello world !"`.
Leave your cursor at the end of the line.

In the Rstudio toolbar, look for the `Addins` menu and click on `Codestral code completion`.

The model answer should appear in your text file starting with `a:`.

## Using codestral package

### Fill in the middle (FIM)

To use the addin, position your cursor at the place you want the FIM to appear 
and look for `Codestral code completion` in the `Addins` list of `RStudio`.

When you click on the addin, the codestral answer is inserted. In the request, the prompt is 
the part of the script before the cursor, the suffix is the part of the script 
after the cursor. The answer is limited to `max_tokens$FIM` as set in `codestral_init`. In case you feel the FIM is incomplete, you may just activate the addin again.

### Chat

- To prompt the Codestral completion functionlity

The current script should start with `c:`. Position your cursor at the end of your question. Activate the addin as for FIM. The answer is inserted from your cursor position.

- To prompt the Mamba completion functionality

Just replace `c:` with `m:`.

The answer will start with `a:`.

You can continue the conversation starting a new line with `c:` or `m:` after the model's answer.

### Including files content

If you wish to include a text file (.R, .Rmd ...) in your prompt, just make sure that the file is in the current working directory or one of its subdirectories (for instance in the same project) and add a line in your prompt starting by "ff:" and followed by the file name : `"ff:my_file.R"`

This will trigger the insertion (behind the scene) of the content of `my_file.R` at the location where the instruction has been placed.

Example:
```
m: Write the necessary unit tests for the following functions
ff:my_fun_file.R
```

### Make it more efficient using keyboard shortcut

In order to define a keyboard shortcut for this addin, in Rstudio, choose the 
menu `Tools/Addins/Brows Addins...` In the pop-up window, click on the Keyboard shortcuts button.
in the new window, double click on the table's cell at row "Codestral code completion" and 
column "Shortcut". Insert your shortcut.

You can now replace default usage by your shortcut.

Additionnaly you may add the initialization step in an `.Rprofile`.

